Verifying Demonstrations

### 2017-08-27 properties.tex
Edits text to be better in text and slides

\begin{frame}
  \begin{remark}
    \begin{itemize}
      \item Unique ring signatures~\cite{UniqueRingSignatures} has this 
        property: two signatures are linked with high probability.
      \item We need keys strongly tied to identities to prevent Sybil.
    \end{itemize}
  \end{remark}

@@

  \begin{remark}
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
    \end{itemize}
  \end{remark}
\end{frame}

>>>>

\begin{frame}
  \begin{remark}
    Unique ring signatures~\cite{UniqueRingSignatures} has this property: two 
    signatures are linked with high probability.
  \end{remark}

@@

  \mode<presentation>{%
    \begin{remark}
      \begin{itemize}
        \item Alice submits her proof.
        \item She stores the hash of the head of the \ac{tposet}.
        \item She removes the proof and signature key.
      \end{itemize}
    \end{remark}
  }
\end{frame}

Say that Alice submits her proof and stores the hash of the head of the 
\ac{tposet} after her proof is included.
Now she can remove her proof and just keep the hash to verify that her proof is 
still there.
She can also remove her signature key, so that Eve cannot use it to reproduce 
the signature using the same inputs.
